---
title: 'R package:blupADC-Feature 1'
author: qsmei
date: '2021-04-14'
slug: blupADC
categories: ["Data format"]
tags: []
subtitle: ''
summary: 'Convert genotype data format'
authors: []
lastmod: '2021-04-14T14:59:41+08:00'
featured: no
image:
  caption: ''
  focal_point: ''
  preview_only: no
projects: []
output:
  blogdown::html_page:
    toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(collapse = TRUE)
```

## Overview 

`genotype_data_format_conversion` is the basic function of  package:`blupADC`.  By applying `genotype_data_format_conversion` , we can convert multiple genotype data formats in an easy way, including Hapmap, Plink, Blupf90, Numeric and VCF.  

**👉 Note:  For analyzing VCF format data,  `blupADC` has encapsulated software Plink `version-1.9` and  VCFtools `version-0.1.17`. If you want change this version, you could set the related parameters in the part of Advanced parameter.**

## Example

```R
library(blupADC)
sum_data=genotype_data_format_conversion(
         input_data_hmp=data_hmp,  #provided hapmap data object 
         output_data_type=c("Plink","Blupf90","Numeric"),# output data format
         return_result = TRUE,      # return result 
         cpu_cores=1                # number of cpu 
         )
```

```{r, echo=FALSE, message=FALSE, warning=FALSE}
library(blupADC)
colnames(data_hmp)[1]="rs#"
data_hmp[1:6,1]=paste0("SNP",1:6)
sum_data=genotype_data_format_conversion(
         input_data_hmp=data_hmp[1:6,],  #provided hapmap data object 
         output_data_type=c("Plink","Blupf90","Numeric"),# output data format
         return_result = TRUE,      # return result 
         cpu_cores=1                # number of cpu 
                  )
```

## Parameter 

### 🤡Primary  

-   **1: input_data_plink_ped**

User-provided  ped format genotype data ，`data.frame` class。

```{r input_data_plink_map2,echo=FALSE}
data_ped=sum_data$ped
data_map=sum_data$map
colnames(data_map)=NULL
data_genumeric=sum_data$genumeric
data_blupf90=sum_data$blupf90
colnames(data_blupf90)=NULL
knitr::kable(head(data_ped[,1:10]))
```

-   **2:input_data_plink_map**

User-provided  map format genotype data ，`data.frame` class。

```{r input_data_plink_map,echo=FALSE}
knitr::kable(head(data_map))
```

-   **3:input_data_hmp**

User-provided  hapmap format genotype data ，`data.frame` class。

```{r input_data_hmp,echo=FALSE}
knitr::kable(head(data_hmp[,1:15]))
```

-   **4:input_data_blupf90**

User-provided  BLUPF90 format genotype data ，`data.frame` class。

```{r input_data_blupf90,echo=FALSE}
knitr::kable(head(data_blupf90))
```

-   **5:input_data_genumeric**

User-provided  Numeric format genotype data ，`matrix(numeric)` class。

```{r input_data_genumeric,echo=FALSE}
knitr::kable(head(data_genumeric[,1:6]))
```

**Note:** rownames stand for individuals，colnames stands for SNPs.  `input_data_genumeric`  should contain both rownames and colnames.

In addition, for convenience, users can provide the  file name, file path, and file type of genotype data directly without reading them in R enviroument by themself .

- **6:input_data_type**

  User-provided  file type of genotype data ，`character` class.

  -   Hapmap
  -   Plink
  -   Blupf90
  -   Numeric
  -   VCF

-   **7:input_data_path**

User-provided  file path of genotype data ，`character` class.

-   **8:input_data_name**

User-provided  file name of genotype data ，`character` class.

**Note:**  if input_data_type is Plink or VCF, user don't need to include suffix in the file name of genotype data. 

eg. for Plink type data, files name are test1.map and test1.ped，we should set`input_data_name="test1"`。

-   **9:return_result**

If return result, `logical` class. Default is FALSE.

Additionally,  for convenience, users can  save output genotype data  into local computer .

-   **10:output_data_path**

File path of output genotype data, `character` class.

-   **11:output_data_name**

File name of output genotype data, `character` class.

-   **12:output_data_type**

    File type of output genotype data, `character` class.

    -   Hapmap
    -   Plink
    -   Blupf90
    -   Numeric
    -   VCF

**Note**: users can  output multiple formats of genotype data simultaneously. e.g.`output_data_type=c("Hapmap","Plink","Blupf90","Numeric")`, outout 4 types of genotype data simultaneously 。

### 💨Secondary

-   **13:cpu_cores**

Number of cpu in calculating,  `numeric`calss. Default is 1.

-   **14:miss_base**

Missing genotype character,  `character`calss. Default is "NN".

-   **15:miss_base_num** 

Missing genotype number after numeric conversion,  `numeric`calss. Default is 5.

-   **16:plink_software_path**

Path of plink software in user computer. `character`calss.

-   **17:plink_software_name**

Name of plink software in user computer. `character`calss.

-   **18:vcftools_software_path**

Path of vcftools software in user computer. `character`calss.

-   **19:vcftools_software_name**

Name of vcftools software in user computer. `character`calss.
