---
title: "blupADC-Genomic prediction(selection)"
subtitle: ''
date: '2023-07-16T10:00:48+08:00'
output: pdf_document
tags: []
categories: []
summary: 'Object-oriented programming in GS of blupADC'
lastmod: '2023-07-16T10:00:48+08:00'
featured: no
draft: no
image:
  caption: ''
  focal_point: ''
  preview_only: no
projects: []
authors: []
---

## blupADC- New features in genomis selection

🤠 In the previous version of blupADC, we have given a comprehensive description of perform BLUP analysis in genomic selection. In order to further simplify the usage of blupADC, we have incorporated R6 package, which supports oriented programming. In the below, we will give server examples of how to perform single trait and multiple traits analysis of PBLUP, GBLUP and ssGBLUP. Also, user can perform cross validation in an easy way in the latest version of blupADC. 

👉 **Note:**  **For the latest version of blupADC, user has to install package `blupSUP` at first, in which example data and software (e.g. DMU and BLUPF90)  are included in this package  **. 

## Example

### Single-trait BLUP model
```{r include=FALSE}

library(blupADC)
```
```{r include=TRUE}
library(blupSUP)
library(blupADC)
data_path=system.file("extdata", package = "blupSUP")
#prepare parameters the BLUP analysis
blup_par=BLUPpar$new(
phe_file=paste0(data_path,"/phenotype.txt"),                                            
phe_colnames=c("Id","Mean","Sex","Herd_Year_Season","Litter","Trait1","Trait2","Age"),
dmu_integer_n=5, #number of integer variable in the phenotype file (required by DMU)
analysis_model="PBLUP_A",
kinship_file=paste0(data_path,"/pedigree.txt"))
#define the model effect  of Trait1
myblup=BLUP$new(fixed=Trait1~Sex+Herd_Year_Season, #fixed effect
                random=~Id+Litter, #random effect 
                pars=blup_par) #blup_par has been defined previously
myblup
```

```{r eval=FALSE}
#BLUP analysis of Trait1
myblup$run(output_path="D:/test",task_type="DMU") # default using DMU 
#myblup$run(output_path="D:/test",task_type="BLUPF90") #using BLUPF90 for analysis 
```

```{r include=FALSE}
#BLUP analysis of Trait1
myblup$run(output_path="D:/test",task_type="DMU") # default using DMU 
#myblup$run(output_path="D:/test",task_type="BLUPF90") #using BLUPF90 for analysis 
```

```{r message=FALSE}
#output of BLUP analysis
ebv=myblup$ebv         #breeding value
h2=myblup$h2   #heritability and its SE
user_defined_h2=myblup$cal_se(~Id1/(Id1+Litter1+Res1)) #user defined expression of calculating h2 based on delta method
```
```{r include=TRUE}
head(ebv)
h2
```
```{r eval=FALSE}
#GBLUP-A analysis 
myblup$pars$kinship_file=paste0(data_path,"/G_Ainv_col_three.txt")
myblup$pars$analysis_model="GBLUP_A"
myblup$run(task_type="DMU")
```

```{r eval=FALSE}
#ssGBLUP-A analysis 
myblup$pars$kinship_file=paste0(data_path,"/",c("pedigree.txt","G_A_col_three.txt"))
myblup$pars$analysis_model="SSBLUP_A"
myblup$run(task_type="DMU")
```

### Multiple traits BLUP  model

``` R
library(blupSUP)
library(blupADC)
data_path=system.file("extdata", package = "blupSUP")
#prepare parameters the BLUP analysis
blup_par=BLUPpar$new(
phe_file=paste0(data_path,"/phenotype.txt"),                                               phe_colnames=c("Id","Mean","Sex","Herd_Year_Season","Litter","Trait1","Trait2","Age"),
dmu_integer_n=5, #number of integer variable in the phenotype file (required by DMU)
analysis_model="PBLUP_A",
kinship_file=paste0(data_path,"/pedigree.txt"))

#define the effect of Trait1 for BLUP analysis
myblup=BLUP$new(fixed=Trait1~Sex+Herd_Year_Season, #fixed effect
               random=~Id+Litter, #random effect 
               pars=blup_par) #blup_par has been defined previously
myblup$run(output_path="D:/test",task_type="DMU") # default using DMU 
myblup
```
``` {r include=FALSE}
library(blupSUP)
library(blupADC)
data_path=system.file("extdata", package = "blupSUP")
#prepare parameters the BLUP analysis
blup_par=BLUPpar$new(
phe_file=paste0(data_path,"/phenotype.txt"),                                               phe_colnames=c("Id","Mean","Sex","Herd_Year_Season","Litter","Trait1","Trait2","Age"),
dmu_integer_n=5, #number of integer variable in the phenotype file (required by DMU)
analysis_model="PBLUP_A",
kinship_file=paste0(data_path,"/pedigree.txt"))

#define the effect of Trait1 for BLUP analysis
myblup=BLUP$new(fixed=Trait1~Sex+Herd_Year_Season, #fixed effect
               random=~Id+Litter, #random effect 
               pars=blup_par) #blup_par has been defined previously
myblup$run(output_path="D:/test",task_type="DMU") # default using DMU 
```

``` {r include=TRUE}
myblup
#Multiple traits analysis
#add model effect of Trait2 in BLUP analysis
myblup$add_model(fixed=Trait2~Herd_Year_Season,random=~Id,covariate=~Age)
myblup
```
``` R
myblup$run() #Multiple traits analysis                 

#remove Trait2 in BLUP analysis 
#myblup$rm_model("Trait2") 

#output of BLUP analysis
ebv=myblup$ebv         #breeding value
h2=myblup$h2   #heritability and its SE
genR2=myblup$r2 #genetic correlation and its SE 
user_defined_h2=myblup$cal_se(~Id1/(Id1+Litter1+Res1)) #user defined expression of calculating h2 based on delta method
user_defined_genR2=myblup$cal_se(~Id1_2/sqrt(Id1 * Id2)) #user defined expression of calculating genR2 based on delta method
#random effect names from multiple traits model were defined in: rownames(myblup$vars_se$vars_mat)         
```

### Cross Validation

``` R
library(blupSUP)
library(blupADC)
data_path=system.file("extdata", package = "blupSUP")

#prepare parameters the BLUP analysis
blup_par=BLUPpar$new(
phe_file=paste0(data_path,"/phenotype.txt"),                                               phe_colnames=c("Id","Mean","Sex","Herd_Year_Season","Litter","Trait1","Trait2","Age"),
dmu_integer_n=5, #number of integer variable in the phenotype file (required by DMU)
analysis_model="PBLUP_A",
kinship_file=paste0(data_path,"/pedigree.txt"))

#define the effect of Trait1 for BLUP analysis
myblup=BLUP$new(fixed=Trait1~Sex+Herd_Year_Season, #fixed effect
                random=~Id+Litter, #random effect 
                pars=blup_par) #blup_par has been defined previously


#define the training and test datasets by holdout 
myCV=CVpredi$new(myblup,  #has been defined previously 
                 partion_type="holdout", #the type of data partioning
                 ratio=0.6) #the ratio of  train_size/(train_size+test_size)

#get the prediction accuracy 
myCV$predict_sets()
accu=myCV$accuracy
bias=myCV$bias
train_set=myCV$datasets$train_sets[[1]] #train set was used in analysis
test_set=myCV$datasets$test_sets[[1]]   #train set was used in analysis 
ebv_set=myCV$datasets$ebv_sets[[1]]   #train set was used in analysis 

#define the training and test datasets by kfold 
myCV=CVpredi$new(myblup,  #has been defined previously 
                 partion_type="kfold", #the type of data partioning
                 ratio=0.6,            #the ratio of  train_size/(train_size+test_size)
                 kfold=5,              #number of fold  
                 seed=9894)            #random seed number for partioning data,default is 9894     

#get the prediction accuracy 
myCV$predict_sets() #perform analysis in all folds 
#myCV$predict_sets(2) # only perform analysis in the first fold 
accu=myCV$accuracy
bias=myCV$bias
train_set2=myCV$datasets$train_sets[[2]] #train set was used in analysis of fold2
test_set2=myCV$datasets$test_sets[[2]]   #train set was used in analysis  of fold2
ebv_set2=myCV$datasets$ebv_sets[[2]]   #train set was used in analysis  of fold2
```

